---
title: "Course Project"
output: html_document
---
Frist loading the data and completing the case impling removing NAs also
I download the data on my computer and extracted it and then read it here
Also changing the data of character to date format.

```{r echo=TRUE}
g<-read.csv("F:\\repdata_data_activity\\activity.csv")
cc<-complete.cases(g)
cd<-g[cc,]
cd$date<-as.Date(cd$date,format = "%Y-%m-%d")
head(cd)
```

Loading the Dplyr library just in case it is needed
second I calculated steps for each date
and then plotted the histogram

```{r echo=TRUE}
library(dplyr)
spd <- aggregate(cd$steps, list(cd$date), FUN=sum)
hist(spd$x,breaks=10,xlab = "Total number of steps taken everyday",main = "Histogram of steps")
```


Now finding the mean and median

```{r echo=TRUE}
mean(spd$x)
median(spd$x)
```

Making a time series plot of the 5-minute interval
For that I aggregated steps with interval from the data also remember the data is 
complete here

```{r echo=TRUE}
spt<-aggregate(cd$steps~cd$interval,data=cd,FUN=mean)
spt$`cd$interval`<-spt$`cd$interval`/100
plot(spt$`cd$interval`,spt$`cd$steps`,type = "l",main = "Average steps Per time interval",xlab = "Time", ylab = "Steps")
```

On average across all the days in the dataset, finding time the maximum number of steps

```{r echo=TRUE}
ms <- tbl_df(spt)
ms %>% select(`cd$steps`,`cd$interval`) %>% filter(`cd$steps` == max(ms$`cd$steps`))
```

Now finding all the missing values in the dataset by taking the complete case 
value and summing it 

```{r echo=TRUE}
mv<-sum(!cc)
print(mv)
```

First changing the data from character to date in original data that I loaded in
g variable I took the mean and replaced the NAs from it as shown in code
and then I made a new dataframe from the newly generated data then I plotted 
the histogram via the same aggregate function as shown
 
```{r echo=TRUE}
g$date<-as.Date(g$date,format = "%Y-%m-%d")
as<-round(mean(spt$`cd$steps`),0) 
g$ns<- ifelse(is.na(g$steps), as , g$steps)
ndf<-data.frame(steps = g$ns,date = g$date, interval = g$interval)
nspd<- aggregate(ndf$steps, list(ndf$date), FUN=sum)
hist(nspd$x,breaks=10,xlab = "Total number of steps taken everyday",main = "Histogram of steps")
```

Now finding mean and median with new data

```{r echo=TRUE}
nme<-mean(nspd$x)
nmed<-median(nspd$x)
```

Now forming new column weekday and daytype
daytype can be weekend or weekday

```{r echo=TRUE}
ndf$weekday<-weekdays(ndf$date)
ndf$daytype<-ifelse(ndf$weekday=='Saturday' | ndf$weekday=='Sunday', 'weekend','weekday')
head(ndf)
```

now aggregated the new data via daytype and plotting the data
two sets of data is made here

```{r echo=TRUE}
nspt<-aggregate(steps~interval+daytype,data=ndf,FUN = mean)
weekd<-filter(nspt,daytype == "weekday")
weeke<-filter(nspt,daytype == "weekend")
```

The first plot is weekday

```{r echo=TRUE}
plot(weekd$interval,weekd$steps,type="l")
```

The second plot is weekend

```{r echo=TRUE}
plot(weeke$interval,weeke$steps,type="l")
```